---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# walking

<!-- badges: start -->
[![R-CMD-check](https://github.com/muschellij2/walking/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/muschellij2/walking/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `walking` is to provide some algorithms to detect walking in tri-axial accelerometers.

## Installation

You can install the development version of walking from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("muschellij2/walking")
```

`walking` no longer tries to install `forest` for you. Install `forest` in
your own Python environment first, then load `walking` from R.

If you hit the LLVM mismatch described in
[onnela-lab/forest#293](https://github.com/onnela-lab/forest/issues/293) and
[numba/llvmlite#1389](https://github.com/numba/llvmlite/issues/1389), use a
Python environment where `forest` and its dependencies already resolve cleanly.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(walking)
csv_file = system.file("test_data_bout.csv", package = "walking")
x = readr::read_csv(csv_file)
colnames(x)[colnames(x) == "UTC time"] = "time"
res = find_walking(data = x)
print(res)
```

## Potential Conflicts

### Running `forest` and [`stepcount`](https://github.com/jhuwit/stepcount). 
The two Python modules (`forest` and `stepcount`) can be be installed in the same `conda` environment, but if they are not, this will lead to an error message.  The options.  One solution is to run them in two separate R sessions (recommended). 

Alternatively, you can try to install `forest` in the `stepcount` conda environment, such as:

```{r, eval = FALSE}
envname = "stepcount2"
stepcount::conda_create_stepcount(envname = envname)
# if you have RETICULATE_PYTHON set
stepcount::unset_reticulate_python()
stepcount::use_stepcount_condaenv(envname = envname)
```

and then run examples such as:

```{r, eval = FALSE}
library(walking)
library(stepcount)
envname = "stepcount2"

# if you have RETICULATE_PYTHON set
stepcount::unset_reticulate_python()
stepcount::use_stepcount_condaenv(envname = envname)

csv_file = system.file("test_data_bout.csv", package = "walking")
x = readr::read_csv(csv_file)
colnames(x)[colnames(x) == "UTC time"] = "time"
res = find_walking(data = x)
```

Remember, however, best practices for Python is "Always create a separate virtual environment for each project" and sometimes one for each "goal".
